Hilbert space methods to approximate Gaussian processes using Stan

### 2019-03-04 Paper/manuscript/manuscript_05.tex
fix inpt encoding problems + microtype

% interacttfssample.tex
% v1.05 - August 2017

\documentclass[]{interact}

@@

% (Paul: This whole paragraph is unclear to me. Are all of these approaches approximations via splines, or are the splines just special cases of a more general method? In any case, I think the paragraph needs substantial revision).
Alternative low-rank approximation is based on forming a basis function approximation with $m \ll$. The basis functions are presented explicitly, but could also be used to form a low rank covariance matrix approximation. Common basis function  approximations are based on the spectral analysis and series expansions of Gaussian processes \citep{loeve1977probability,trees1968detection,adler1981geometry,cramer2013stationary}.
Certain spline smoothing basis functions are equivalent to GPs with certain covariance function \citep{wahba1990spline}, but not all spline models are GPs (sometimes splines are not marginalization consistent)-
%
The sparse spectrum GPs are based on a sparse approximation to the frequency domain representation of a GP \citep{lazaro2010sparse,quia2010sparse,gal2015improving,gal2015improving}. Recently \citep{hensman2017variational} presented a variational Fourier feature approximation for Gaussian processes that was derived for the Mat´ern class of kernels. Random fourier features \citep{rahimi2008random,rahimi2009weighted} is a method for approximating kernels.

@@

The approach based on inducing points employs a small set of pseudo data points to summarise the actual data. The storage requirements are reduced to $O(nm)$ and complexity to $O(nm^2)$, where $m < n$. Some of these methods have been reviewed in \cite{rasmussen2006gaussian}, and \cite{quinonero2005unifying} provide a unifying view of these methods based on approximate generative methods. From a spectral point of view, several of these methods (e.g., SOR, DTC, VAR, FIC) can be interpreted as modiﬁcations to the so-called Nystr\"om method (see \cite{arthur1979baker} and \cite{williams2001using}), a scheme for approximating the eigenspectrum. These methods are basically based on choosing a set of $m$ inducing inputs $x_u$ and scaling the corresponding eigendecomposition of their corresponding covariance matrix $K_{u,u}$ to match that of the actual covariance.

@@

Recently \citep{hensman2017variational} presented a variational Fourier feature approximation for Gaussian processes that was derived for the Mat´ern class of kernels, where the approximation structure is set up by a low-rank plus diagonal structure. They combine the variational methodology with Fourier based approximations.

>>>>

% interacttfssample.tex
% v1.05 - August 2017
\documentclass[]{interact}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{microtype}

@@

% (Paul: This whole paragraph is unclear to me. Are all of these approaches approximations via splines, or are the splines just special cases of a more general method? In any case, I think the paragraph needs substantial revision).
Alternative low-rank approximation is based on forming a basis function approximation with $m \ll$. The basis functions are presented explicitly, but could also be used to form a low rank covariance matrix approximation. Common basis function  approximations are based on the spectral analysis and series expansions of Gaussian processes \citep{loeve1977probability,trees1968detection,adler1981geometry,cramer2013stationary}.
Certain spline smoothing basis functions are equivalent to GPs with certain covariance function \citep{wahba1990spline}, but not all spline models are GPs (sometimes splines are not marginalization consistent)-
%
The sparse spectrum GPs are based on a sparse approximation to the frequency domain representation of a GP \citep{lazaro2010sparse,quia2010sparse,gal2015improving,gal2015improving}. Recently \citep{hensman2017variational} presented a variational Fourier feature approximation for Gaussian processes that was derived for the Mat{\'e}rn class of kernels. Random fourier features \citep{rahimi2008random,rahimi2009weighted} is a method for approximating kernels.

@@

The approach based on inducing points employs a small set of pseudo data points to summarise the actual data. The storage requirements are reduced to $O(nm)$ and complexity to $O(nm^2)$, where $m < n$. Some of these methods have been reviewed in \cite{rasmussen2006gaussian}, and \cite{quinonero2005unifying} provide a unifying view of these methods based on approximate generative methods. From a spectral point of view, several of these methods (e.g., SOR, DTC, VAR, FIC) can be interpreted as modfications to the so-called Nystr{\"o}m method (see \cite{arthur1979baker} and \cite{williams2001using}), a scheme for approximating the eigenspectrum. These methods are basically based on choosing a set of $m$ inducing inputs $x_u$ and scaling the corresponding eigendecomposition of their corresponding covariance matrix $K_{u,u}$ to match that of the actual covariance.

@@

Recently \citep{hensman2017variational} presented a variational Fourier feature approximation for Gaussian processes that was derived for the Mat{\'e}rn class of kernels, where the approximation structure is set up by a low-rank plus diagonal structure. They combine the variational methodology with Fourier based approximations.
